```{r}
#Correlation Code and Rough Draft Models, Uses FinalDat2

require(TeachingDemos)
require(caTools)

FinalDat2$pressure1224<-FinalDat2$pressure_12h_Den-FinalDat2$pressure_24h_Den
FinalDat2$humidity1224<-FinalDat2$humidity_12h_Den-FinalDat2$humidity_24h_Den
FinalDat2$temp1224<-FinalDat2$temp_12h_Den-FinalDat2$temp_24h_Den
FinalDat2$wind_speed1224<-FinalDat2$wind_speed_12h_Den-FinalDat2$wind_speed_24h_Den
FinalDat2$clouds_all1224<-FinalDat2$clouds_all_12h_Den-FinalDat2$clouds_all_24h_Den

FinalDat2$pressure624<-FinalDat2$pressure_6h_Den-FinalDat2$pressure_24h_Den
FinalDat2$humidity624<-FinalDat2$humidity_6h_Den-FinalDat2$humidity_24h_Den
FinalDat2$temp624<-FinalDat2$temp_6h_Den-FinalDat2$temp_24h_Den
FinalDat2$wind_speed624<-FinalDat2$wind_speed_6h_Den-FinalDat2$wind_speed_24h_Den
FinalDat2$clouds_all624<-FinalDat2$clouds_all_6h_Den-FinalDat2$clouds_all_24h_Den

FinalDat2$pressure324<-FinalDat2$pressure_3h_Den-FinalDat2$pressure_24h_Den
FinalDat2$humidity324<-FinalDat2$humidity_3h_Den-FinalDat2$humidity_24h_Den
FinalDat2$temp324<-FinalDat2$temp_3h_Den-FinalDat2$temp_24h_Den
FinalDat2$wind_speed324<-FinalDat2$wind_speed_3h_Den-FinalDat2$wind_speed_24h_Den
FinalDat2$clouds_all324<-FinalDat2$clouds_all_3h_Den-FinalDat2$clouds_all_24h_Den

FinalDat2$pressure124<-FinalDat2$pressure_1h_Den-FinalDat2$pressure_24h_Den
FinalDat2$humidity124<-FinalDat2$humidity_1h_Den-FinalDat2$humidity_24h_Den
FinalDat2$temp124<-FinalDat2$temp_1h_Den-FinalDat2$temp_24h_Den
FinalDat2$wind_speed124<-FinalDat2$wind_speed_1h_Den-FinalDat2$wind_speed_24h_Den
FinalDat2$clouds_all124<-FinalDat2$clouds_all_1h_Den-FinalDat2$clouds_all_24h_Den

FinalDat2$pressure612<-FinalDat2$pressure_6h_Den-FinalDat2$pressure_12h_Den
FinalDat2$humidity612<-FinalDat2$humidity_6h_Den-FinalDat2$humidity_12h_Den
FinalDat2$temp612<-FinalDat2$temp_6h_Den-FinalDat2$temp_12h_Den
FinalDat2$wind_speed612<-FinalDat2$wind_speed_6h_Den-FinalDat2$wind_speed_12h_Den
FinalDat2$clouds_all612<-FinalDat2$clouds_all_6h_Den-FinalDat2$clouds_all_12h_Den

FinalDat2$pressure312<-FinalDat2$pressure_3h_Den-FinalDat2$pressure_12h_Den
FinalDat2$humidity312<-FinalDat2$humidity_3h_Den-FinalDat2$humidity_12h_Den
FinalDat2$temp312<-FinalDat2$temp_3h_Den-FinalDat2$temp_12h_Den
FinalDat2$wind_speed312<-FinalDat2$wind_speed_3h_Den-FinalDat2$wind_speed_12h_Den
FinalDat2$clouds_all312<-FinalDat2$clouds_all_3h_Den-FinalDat2$clouds_all_12h_Den

FinalDat2$pressure112<-FinalDat2$pressure_1h_Den-FinalDat2$pressure_12h_Den
FinalDat2$humidity112<-FinalDat2$humidity_1h_Den-FinalDat2$humidity_12h_Den
FinalDat2$temp112<-FinalDat2$temp_1h_Den-FinalDat2$temp_12h_Den
FinalDat2$wind_speed112<-FinalDat2$wind_speed_1h_Den-FinalDat2$wind_speed_12h_Den
FinalDat2$clouds_all112<-FinalDat2$clouds_all_1h_Den-FinalDat2$clouds_all_12h_Den

FinalDat2$pressure36<-FinalDat2$pressure_3h_Den-FinalDat2$pressure_6h_Den
FinalDat2$humidity36<-FinalDat2$humidity_3h_Den-FinalDat2$humidity_6h_Den
FinalDat2$temp36<-FinalDat2$temp_3h_Den-FinalDat2$temp_6h_Den
FinalDat2$wind_speed36<-FinalDat2$wind_speed_3h_Den-FinalDat2$wind_speed_6h_Den
FinalDat2$clouds_all36<-FinalDat2$clouds_all_3h_Den-FinalDat2$clouds_all_6h_Den

FinalDat2$pressure16<-FinalDat2$pressure_1h_Den-FinalDat2$pressure_6h_Den
FinalDat2$humidity16<-FinalDat2$humidity_1h_Den-FinalDat2$humidity_6h_Den
FinalDat2$temp16<-FinalDat2$temp_1h_Den-FinalDat2$temp_6h_Den
FinalDat2$wind_speed16<-FinalDat2$wind_speed_1h_Den-FinalDat2$wind_speed_6h_Den
FinalDat2$clouds_all16<-FinalDat2$clouds_all_1h_Den-FinalDat2$clouds_all_6h_Den

FinalDat2$pressure13<-FinalDat2$pressure_1h_Den-FinalDat2$pressure_3h_Den
FinalDat2$humidity13<-FinalDat2$humidity_1h_Den-FinalDat2$humidity_3h_Den
FinalDat2$temp13<-FinalDat2$temp_1h_Den-FinalDat2$temp_3h_Den
FinalDat2$wind_speed13<-FinalDat2$wind_speed_1h_Den-FinalDat2$wind_speed_3h_Den
FinalDat2$clouds_all13<-FinalDat2$clouds_all_1h_Den-FinalDat2$clouds_all_3h_Den
View(FinalDat2)
names(FinalDat2)

datsleek<-FinalDat2[-c(1,3,4,13,14,19,31,32,44,45,57,58,70,71,83)]
View(datsleek)
datnum<-datsleek[-c(15,16,26,27,37,38,48,49,59,60)]
View(datnum)

View(datnum)
ncol(datnum)
save(datsleek, file = "datsleek.rda")
save(datnum, file = "datnum.rda")

correlations<-cor(datnum)
correlations[lower.tri(correlations,diag=TRUE)]=NA
correlations=as.data.frame(as.table(correlations))
correlations=na.omit(correlations)
correlations=correlations[order(-abs(correlations$Freq)),]
print(correlations)
write.csv(correlations,file="correlations.csv")

hour24<-datnum
hour12<-datnum
hour6<-datnum
hour3<-datnum
hour1<-datnum

hour24<-hour24[c(50:59,64,70)]
hour24<-hour24[-c(12)]
names(hour24)
hour12<-hour12[c(41:49,59,63,64,69,71:75)]
hour12<-hour12[-c(13)]
names(hour12)
hour6<-hour6[c(32:40,59,62:64,68,76:80,91:95)]
hour6<-hour6[-c(14)]
names(hour6)
hour3<-hour3[c(23:31,59,61:64,67,81:85,96:100,106:110)]
hour3<-hour3[-c(15)]
names(hour3)
hour1<-hour1[c(14:22,59,60:64,66:70,86:90,101:105.111:120)]
hour1<-hour1[-c(17:20)]
hour1<-hour1[-c(31)]
hour1<-hour1[-c(16)]
hour1<-hour1[-c(26:29)]
names(hour1)
```


```{r}
pairs2(hour24[1:6],hour24[1:6])
pairs2(hour24 [1:6], hour24 [7:11])
pairs2(hour24 [7:11], hour24 [7:11])
```

```{r}
corr24<-cor(hour24)
corr24[lower.tri(corr24,diag=TRUE)]=NA
corr24=as.data.frame(as.table(corr24))
corr24=na.omit(corr24)
corr24=corr24[order(-abs(corr24$Freq)),]
print(corr24)
write.csv(corr24,file="corr24.csv")

corr12<-cor(hour12)
corr12[lower.tri(corr12,diag=TRUE)]=NA
corr12=as.data.frame(as.table(corr12))
corr12=na.omit(corr12)
corr12=corr12[order(-abs(corr12$Freq)),]
print(corr12)
write.csv(corr12,file="corr12.csv")

corr6<-cor(hour6)
corr6[lower.tri(corr6,diag=TRUE)]=NA
corr6=as.data.frame(as.table(corr6))
corr6=na.omit(corr6)
corr6=corr6[order(-abs(corr6$Freq)),]
print(corr6)
write.csv(corr6,file="corr6.csv")

corr3<-cor(hour3)
corr3[lower.tri(corr3,diag=TRUE)]=NA
corr3=as.data.frame(as.table(corr3))
corr3=na.omit(corr3)
corr3=corr3[order(-abs(corr3$Freq)),]
print(corr3)
write.csv(corr3,file="corr3.csv")

corr1<-cor(hour1)
corr1[lower.tri(corr1,diag=TRUE)]=NA
corr1=as.data.frame(as.table(corr1))
corr1=na.omit(corr1)
corr1=corr1[order(-abs(corr1$Freq)),]
print(corr1)
write.csv(corr1,file="corr1.csv")

attach(FinalDat2)

########
24
Hour
Model
############
ans24hrs<-glm(as.factor(Question)~temp_24h_Den
+pressure_24h_Den+humidity_24h_Den
+weather_main_24h_Den_Dummy,
family=binomial(),
data=trainset)
summary(ans24hrs)
coef(ans24hrs)
summary(ans24hrs)$coef
summary(ans24hrs)$coef[,4]
glm.probs=predict(ans24hrs,type="response")
glm.probs[1:10]
summary(ans24hrs)

########
12
Hour
Model
############
ans12hrs<-
glm(as.factor(Question)
~
temp_12h_Den
+pressure_12h_Den+humidity_12h_Den+wind_speed_12h_Den+wind_dir_12h_Den
+rain_1h_12h_Den+rain_3h_12h_Den+snow_1h_12h_Den
+snow_3h_12h_Den+clouds_all_12h_Den
+weather_main_12h_Den_Dummy
+I((pressure_12h_Den-pressure_24h_Den)/(24-12))
+I((temp_12h_Den-temp_24h_Den)/(24-12))
+I((humidity_12h_Den-humidity_24h_Den)/(24-12))
+I((wind_speed_12h_Den-wind_speed_24h_Den)/(24-12))
,
family=binomial(),
data=trainset)
summary(ans12hrs)
########
6
Hour
Model
############
ans6hrs<-
glm(as.factor(Question)
~
temp_6h_Den
+pressure_6h_Den+humidity_6h_Den+wind_speed_6h_Den+wind_dir_6h_Den
+rain_1h_6h_Den+rain_3h_6h_Den+snow_1h_6h_Den
+snow_3h_6h_Den+clouds_all_6h_Den
+weather_main_6h_Den_Dummy
+I((pressure_6h_Den-pressure_24h_Den)/(24-6))
+I((temp_6h_Den-temp_24h_Den)/(24-6))
+I((humidity_6h_Den-humidity_24h_Den)/(24-6))
+I((wind_speed_6h_Den-wind_speed_24h_Den)/(24-6))
+I((pressure_6h_Den-pressure_12h_Den)/(12-6))
+I((temp_6h_Den-temp_12h_Den)/(12-6))
+I((humidity_6h_Den-humidity_12h_Den)/(12-6))
+I((wind_speed_6h_Den-wind_speed_12h_Den)/(12-6))
,
family=binomial(),
data=trainset)
summary(ans6hrs)
plot(ans6hrs)
########
3
Hour
Model
############
ans3hrs<-
glm(as.factor(Question)
~
temp_3h_Den
+pressure_3h_Den+humidity_3h_Den+wind_speed_3h_Den+wind_dir_3h_Den
+rain_1h_3h_Den+rain_3h_3h_Den+snow_1h_3h_Den
+snow_3h_3h_Den+clouds_all_3h_Den
+weather_main_3h_Den_Dummy
+I((pressure_3h_Den-pressure_24h_Den)/(24-3))
+I((temp_3h_Den-temp_24h_Den)/(24-3))
+I((humidity_3h_Den-humidity_24h_Den)/(24-3))
+I((wind_speed_3h_Den-wind_speed_24h_Den)/(24-3))
+I((pressure_3h_Den-pressure_12h_Den)/(12-3))
+I((temp_3h_Den-temp_12h_Den)/(12-3))
+I((humidity_3h_Den-humidity_12h_Den)/(12-3))
+I((wind_speed_3h_Den-wind_speed_12h_Den)/(12-3))
+I((pressure_3h_Den-pressure_6h_Den)/(6-3))
+I((temp_3h_Den-temp_6h_Den)/(6-3))
+I((humidity_3h_Den-humidity_6h_Den)/(6-3))
+I((wind_speed_3h_Den-wind_speed_6h_Den)/(6-3))
,
family=binomial(),
data=trainset)
summary(ans3hrs)
plot(ans3hrs)
########
1
Hour
Model
############
ans1hrs<-
glm(as.factor(Question)
~
temp_1h_Den
+pressure_1h_Den+humidity_1h_Den+wind_speed_1h_Den+wind_dir_1h_Den
+rain_1h_1h_Den+rain_3h_1h_Den+snow_1h_1h_Den
+snow_3h_1h_Den+clouds_all_1h_Den
+weather_main_1h_Den_Dummy
+I((pressure_1h_Den-pressure_24h_Den)/(24-1))
+I((temp_1h_Den-temp_24h_Den)/(24-1))
+I((humidity_1h_Den-humidity_24h_Den)/(24-1))
+I((wind_speed_1h_Den-wind_speed_24h_Den)/(24-1))
+I((pressure_1h_Den-pressure_12h_Den)/(12-1))
+I((temp_1h_Den-temp_12h_Den)/(12-1))
+I((humidity_1h_Den-humidity_12h_Den)/(12-1))
+I((wind_speed_1h_Den-wind_speed_12h_Den)/(12-1))
+I((pressure_1h_Den-pressure_6h_Den)/(6-1))
+I((temp_1h_Den-temp_6h_Den)/(6-1))
+I((humidity_1h_Den-humidity_6h_Den)/(6-1))
+I((wind_speed_1h_Den-wind_speed_6h_Den)/(6-1))
+I((pressure_1h_Den-pressure_3h_Den)/(3-1))
+I((temp_1h_Den-temp_3h_Den)/(3-1))
+I((humidity_1h_Den-humidity_3h_Den)/(3-1))
+I((wind_speed_1h_Den-wind_speed_3h_Den)/(3-1))
,
family=binomial(),
data=trainset)
summary(ans1hrs)
plot(ans1hrs)

