---
output:
  pdf_document: default
  html_document: default
---
Clear working environment, Set Working Directory to Variable WD
```{r}
rm(list=ls())
WD="/Users/lee/Documents/GitHub/new_weather_data"
setwd(WD)
```

Load Libraries & Install Packages
```{r}
install.packages("lubridate")
library(lubridate)
```

Load NewData.csv, create new Data sets:Denver and CrestedButte for each citie's data
```{r include=FALSE}
NewData <- read.csv("NewData.csv")
summary(NewData)
subset1<-subset(NewData, city_id == '5418523')
subset2<-subset(NewData, city_id == '5419384')
Denver<-subset1
CrestedButte<-subset2
rm(subset1)
rm(subset2)
```

Set NA measurements to zero, and converting city names to factors, with city-NA removals
```{r include=FALSE}
Denver$snow_3h[is.na(Denver$snow_3h)] <- 0
CrestedButte$snow_3h[is.na(CrestedButte$snow_3h)] <- 0

Denver$snow_1h[is.na(Denver$snow_1h)] <- 0
CrestedButte$snow_1h[is.na(CrestedButte$snow_1h)] <- 0

Denver$rain_3h[is.na(Denver$rain_3h)] <- 0
CrestedButte$rain_3h[is.na(CrestedButte$rain_3h)] <- 0

Denver$rain_1h[is.na(Denver$rain_1h)] <- 0
CrestedButte$rain_1h[is.na(CrestedButte$rain_1h)] <- 0

Denver$city_name[is.na(Denver$city_name)] <- 'Denver'
CrestedButte$city_name[is.na(CrestedButte$city_name)] <- 'CrestedButte'

Denver$city_name <- as.factor(Denver$city_name)
CrestedButte$city_name <- as.factor(CrestedButte$city_name)

Denver$lat[is.na(Denver$lat)] <- 39.7392
CrestedButte$lat[is.na(CrestedButte$lat)] <- 38.8697
Denver$lon[is.na(Denver$lon)] <- -104.9848
CrestedButte$lon[is.na(CrestedButte$lon)] <- -106.9879
```

Initial Data Summaries, and Saving new .RDA data sets to WD file for Denver and CrestedButte
```{r include=FALSE}
summary(Denver)
summary(CrestedButte)

save(Denver, file = "Denver.rda")
save(CrestedButte, file = "CrestedButte.rda")

# model<-lm(rain_3h~temp+pressure+humidity+wind_speed,Denver)
# summary(model)
# 
# Denver_sample<-Denver[sample(nrow(Denver), 500), ]
# 
# model<-lm(rain_3h~temp+pressure+humidity+wind_speed,Denver_sample)
# summary(model)
```

Create Time-Formatting variable data for Denver data
```{r include=FALSE}
dt_iso_col_denver=Denver$dt_iso
year_Den=year(dt_iso_col_denver)
month_Den=month(dt_iso_col_denver)
day_Den=day(dt_iso_col_denver)
hour_Den=hour(dt_iso_col_denver)
Denver$Year=NA
Denver$Year=year_Den
Denver$Month=NA
Denver$Month=month_Den
Denver$Day=NA
Denver$Day=day_Den
Denver$Hour=NA
Denver$Hour=hour_Den
rm(dt_iso_col_denver)
rm(year_Den)
rm(month_Den)
rm(day_Den)
rm(hour_Den)
```

<!-- Create Time-Formatting variable data for CB data -->
<!-- ```{r include=FALSE} -->
<!-- dt_iso_col_CB=CrestedButte$dt_iso -->
<!-- year_CB=year(dt_iso_col_CB) -->
<!-- month_CB=month(dt_iso_col_CB) -->
<!-- day_CB=day(dt_iso_col_CB) -->
<!-- hour_CB=hour(dt_iso_col_CB) -->
<!-- CrestedButte$Year=NA -->
<!-- CrestedButte$Year=year_CB -->
<!-- CrestedButte$Month=NA -->
<!-- CrestedButte$Month=month_CB -->
<!-- CrestedButte$Day=NA -->
<!-- CrestedButte$Day=day_CB -->
<!-- CrestedButte$Hour=NA -->
<!-- CrestedButte$Hour=hour_CB -->
<!-- rm(dt_iso_col_CB) -->
<!-- rm(year_CB) -->
<!-- rm(month_CB) -->
<!-- rm(day_CB) -->
<!-- rm(hour_CB) -->
<!-- ``` -->

Create -1H, -3H, -6H, -12H, -24H Time indicator columns for Denver data
```{r include=FALSE}
Denver$ind_1=NA
Denver$ind_3=NA
Denver$ind_6=NA
Denver$ind_12=NA
Denver$ind_24=NA


for (i in 2:35888)
{ 
    if((Denver$Hour[i-1]+1==Denver$Hour[i]) | (Denver$Hour[i-1]==23 & Denver$Hour[i]==0))
    {Denver$ind_1[i]=1}
    else
    {Denver$ind_1[i]=0}
}


for(i in 4:35888)
{
    if((Denver$Hour[i-3]+3==Denver$Hour[i]) | (Denver$Hour[i-3]==23 & Denver$Hour[i]==2))
    {Denver$ind_3[i]=3}
    else
    {Denver$ind_3[i]=0}
}

for(i in 7:35888)
{
    if((Denver$Hour[i-6]+6==Denver$Hour[i]) | (Denver$Hour[i-6]==23 & Denver$Hour[i]==5))
    {Denver$ind_6[i]=6}
    else
    {Denver$ind_6[i]=0}
}

for(i in 13:35888)
{
    if((Denver$Hour[i-12]+12==Denver$Hour[i]) | (Denver$Hour[i-12]==23 & Denver$Hour[i]==11))
    {Denver$ind_12[i]=12}
    else
    {Denver$ind_12[i]=0}
}

for(i in 25:35888)
{
    if((Denver$Hour[i-24]+24==Denver$Hour[i]) | (Denver$Hour[i-24]==23 & Denver$Hour[i]==23))
    {Denver$ind_24[i]=24}
    else
    {Denver$ind_24[i]=0}
}
```

Create New -1H-Denver Data Set
```{r}
dt_1h_Den=c()         
temp_1h_Den=c()              
temp_min_1h_Den=c()     
temp_max_1h_Den=c()        
pressure_1h_Den=c()           
humidity_1h_Den=c()           
wind_speed_1h_Den=c()      
wind_deg_1h_Den=c()          
rain_1h_1h_Den=c()            
rain_3h_1h_Den=c()           
snow_1h_1h_Den=c()            
snow_3h_1h_Den=c()            
clouds_all_1h_Den=c()          
weather_id_1h_Den=c()         
weather_main_1h_Den=c()      
weather_description_1h_Den=c() 


for(i in 2:3588)
{ 
  if (Denver$ind_1[i]==1)
  {
    dt_1h_Den[i]=Denver$dt[i-1]         
    temp_1h_Den[i]=Denver$temp[i-1]              
    temp_min_1h_Den[i]=Denver$temp_min[i-1]     
    temp_max_1h_Den[i]=Denver$temp_max[i-1]        
    pressure_1h_Den[i]=Denver$pressure[i-1]           
    humidity_1h_Den[i]=Denver$humidity[i-1]           
    wind_speed_1h_Den[i]=Denver$wind_speed[i-1]      
    wind_deg_1h_Den[i]=Denver$wind_deg[i-1]          
    rain_1h_1h_Den[i]=Denver$rain_1h[i-1]            
    rain_3h_1h_Den[i]=Denver$rain_3h[i-1]           
    snow_1h_1h_Den[i]=Denver$snow_1h[i-1]            
    snow_3h_1h_Den[i]=Denver$snow_3h[i-1]            
    clouds_all_1h_Den[i]=Denver$clouds_all[i-1]          
    weather_id_1h_Den[i]=Denver$weather_id[i-1]         
    weather_main_1h_Den[i]=Denver$weather_main[i-1]      
    weather_description_1h_Den[i]=Denver$weather_description[i-1] 
  }
}

Denver_1H=data.frame(dt_1h_Den,         
                     temp_1h_Den,              
                     temp_min_1h_Den,     
                     temp_max_1h_Den,        
                     pressure_1h_Den,         
                     humidity_1h_Den,           
                     wind_speed_1h_Den,      
                     wind_deg_1h_Den,          
                     rain_1h_1h_Den,            
                     rain_3h_1h_Den,           
                     rain_24h_1h_Den,         
                     snow_1h_1h_Den,            
                     snow_3h_1h_Den,            
                     clouds_all_1h_Den,          
                     weather_id_1h_Den,         
                     weather_main_1h_Den,      
                     weather_description_1h_Den) 
save(Denver_1H, file = 'Denver_1H.rda')
```


Create New -3H-Denver Data Set
```{r}
dt_3h_Den=c()         
temp_3h_Den=c()              
temp_min_3h_Den=c()     
temp_max_3h_Den=c()        
pressure_3h_Den=c()           
sea_level_3h_Den=c()    
grnd_level_3h_Den=c()    
humidity_3h_Den=c()           
wind_speed_3h_Den=c()      
wind_deg_3h_Den=c()          
rain_1h_3h_Den=c()            
rain_3h_3h_Den=c()           
rain_24h_3h_Den=c()         
rain_today_3h_Den=c()         
snow_1h_3h_Den=c()            
snow_3h_3h_Den=c()            
snow_24h_3h_Den=c()           
snow_today_3h_Den=c()         
clouds_all_3h_Den=c()          
weather_id_3h_Den=c()         
weather_main_3h_Den=c()      
weather_description_3h_Den=c() 
weather_icon_3h_Den=c()


for(i in 2:3588)
{ 
  if (Denver$ind_1[i]==1)
  {
    dt_3h_Den[i]=Denver$dt[i-1]         
    temp_3h_Den[i]=Denver$temp[i-1]              
    temp_min_3h_Den[i]=Denver$temp_min[i-1]     
    temp_max_3h_Den[i]=Denver$temp_max[i-1]        
    pressure_3h_Den[i]=Denver$pressure[i-1]           
    sea_level_3h_Den[i]=Denver$sea_level[i-1]    
    grnd_level_3h_Den[i]=Denver$grnd_level[i-1]    
    humidity_3h_Den[i]=Denver$humidity[i-1]           
    wind_speed_3h_Den[i]=Denver$wind_speed[i-1]      
    wind_deg_3h_Den[i]=Denver$wind_deg[i-1]          
    rain_1h_3h_Den[i]=Denver$rain_1h[i-1]            
    rain_3h_3h_Den[i]=Denver$rain_3h[i-1]           
    rain_24h_3h_Den[i]=Denver$rain_24h[i-1]         
    rain_today_3h_Den[i]=Denver$rain_today[i-1]         
    snow_1h_3h_Den[i]=Denver$snow_1h[i-1]            
    snow_3h_3h_Den[i]=Denver$snow_3h[i-1]            
    snow_24h_3h_Den[i]=Denver$snow_24h[i-1]           
    snow_today_3h_Den[i]=Denver$snow_today[i-1]         
    clouds_all_3h_Den[i]=Denver$clouds_all[i-1]          
    weather_id_3h_Den[i]=Denver$weather_id[i-1]         
    weather_main_3h_Den[i]=Denver$weather_main[i-1]      
    weather_description_3h_Den[i]=Denver$weather_description[i-1] 
    weather_icon_3h_Den[i]=Denver$weather_icon[i-1]
  }
}

Denver_3h=data.frame(dt_3h_Den,         
                     temp_3h_Den,              
                     temp_min_3h_Den,     
                     temp_max_3h_Den,        
                     pressure_3h_Den,           
                     sea_level_3h_Den,    
                     grnd_level_3h_Den,    
                     humidity_3h_Den,           
                     wind_speed_3h_Den,      
                     wind_deg_3h_Den,          
                     rain_1h_3h_Den,            
                     rain_3h_3h_Den,           
                     rain_24h_3h_Den,         
                     rain_today_3h_Den,         
                     snow_1h_3h_Den,            
                     snow_3h_3h_Den,            
                     snow_24h_3h_Den,           
                     snow_today_3h_Den,         
                     clouds_all_3h_Den,          
                     weather_id_3h_Den,         
                     weather_main_3h_Den,      
                     weather_description_3h_Den, 
                     weather_icon_3h_Den)
save(Denver_3h, file = 'Denver_3h.rda')
```


Create New -6H-Denver Data Set
```{r}
# dt         
# dt_iso      
# city_id          
# city_name        
# lat                
# lon           
# temp              
# temp_min     
# temp_max        
# pressure           
# sea_level    
# grnd_level    
# humidity           
# wind_speed      
# wind_deg          
# rain_1h            
# rain_3h           
# rain_24h         
# rain_today         
# snow_1h            
# snow_3h            
# snow_24h           
# snow_today         
# clouds_all          
# weather_id         
# weather_main      
# weather_description 
# weather_icon


dt_3h_Den=c()         
temp_3h_Den=c()              
temp_min_3h_Den=c()     
temp_max_3h_Den=c()        
pressure_3h_Den=c()           
sea_level_3h_Den=c()    
grnd_level_3h_Den=c()    
humidity_3h_Den=c()           
wind_speed_3h_Den=c()      
wind_deg_3h_Den=c()          
rain_1h_3h_Den=c()            
rain_3h_3h_Den=c()           
rain_24h_3h_Den=c()         
rain_today_3h_Den=c()         
snow_1h_3h_Den=c()            
snow_3h_3h_Den=c()            
snow_24h_3h_Den=c()           
snow_today_3h_Den=c()         
clouds_all_3h_Den=c()          
weather_id_3h_Den=c()         
weather_main_3h_Den=c()      
weather_description_3h_Den=c() 
weather_icon_3h_Den=c()


for(i in 2:3588)
{ 
  if (Denver$ind_1[i]==1)
  {
    dt_3h_Den[i]=Denver$dt[i-1]         
    temp_3h_Den[i]=Denver$temp[i-1]              
    temp_min_3h_Den[i]=Denver$temp_min[i-1]     
    temp_max_3h_Den[i]=Denver$temp_max[i-1]        
    pressure_3h_Den[i]=Denver$pressure[i-1]           
    sea_level_3h_Den[i]=Denver$sea_level[i-1]    
    grnd_level_3h_Den[i]=Denver$grnd_level[i-1]    
    humidity_3h_Den[i]=Denver$humidity[i-1]           
    wind_speed_3h_Den[i]=Denver$wind_speed[i-1]      
    wind_deg_3h_Den[i]=Denver$wind_deg[i-1]          
    rain_1h_3h_Den[i]=Denver$rain_1h[i-1]            
    rain_3h_3h_Den[i]=Denver$rain_3h[i-1]           
    rain_24h_3h_Den[i]=Denver$rain_24h[i-1]         
    rain_today_3h_Den[i]=Denver$rain_today[i-1]         
    snow_1h_3h_Den[i]=Denver$snow_1h[i-1]            
    snow_3h_3h_Den[i]=Denver$snow_3h[i-1]            
    snow_24h_3h_Den[i]=Denver$snow_24h[i-1]           
    snow_today_3h_Den[i]=Denver$snow_today[i-1]         
    clouds_all_3h_Den[i]=Denver$clouds_all[i-1]          
    weather_id_3h_Den[i]=Denver$weather_id[i-1]         
    weather_main_3h_Den[i]=Denver$weather_main[i-1]      
    weather_description_3h_Den[i]=Denver$weather_description[i-1] 
    weather_icon_3h_Den[i]=Denver$weather_icon[i-1]
  }
}

Denver_3h=data.frame(dt_3h_Den,         
                     temp_3h_Den,              
                     temp_min_3h_Den,     
                     temp_max_3h_Den,        
                     pressure_3h_Den,           
                     sea_level_3h_Den,    
                     grnd_level_3h_Den,    
                     humidity_3h_Den,           
                     wind_speed_3h_Den,      
                     wind_deg_3h_Den,          
                     rain_1h_3h_Den,            
                     rain_3h_3h_Den,           
                     rain_24h_3h_Den,         
                     rain_today_3h_Den,         
                     snow_1h_3h_Den,            
                     snow_3h_3h_Den,            
                     snow_24h_3h_Den,           
                     snow_today_3h_Den,         
                     clouds_all_3h_Den,          
                     weather_id_3h_Den,         
                     weather_main_3h_Den,      
                     weather_description_3h_Den, 
                     weather_icon_3h_Den)
save(Denver_3h, file = 'Denver_3h.rda')
```








