```{r}
require(caTools)
dat<-FinalDat2
dat<-FinalDat2[-c(1,14,90:95)]
set.seed(101) 
dat_sample<-dat[sample(nrow(dat), 3000), ]
sample = sample.split(dat_sample$pressure, SplitRatio = .75)
trainset = subset(dat_sample, sample == TRUE)
testset  = subset(dat_sample, sample == FALSE)

mean_train<-apply(trainset, 2, mean)
var_train<-apply(trainset, 2, var)

train <- t((t(trainset)-mean_train)/sqrt(var_train))
apply(train, 2, mean)
apply(train, 2, var)

dat.train<-data.frame(train, Question=trainset$Question)

##	NEED TO APPLY TRAINING MEAN AND STDEV TO STANDARDIZE TEST SET!!  ##
test<-as.data.frame(t((t(testset)-mean_train)/sqrt(var_train)))
dat.test <- data.frame(test, Question=testset$Question)
apply(test, 2, mean)
apply(test, 2, var)



dat.train24x <- names(dat.train) %in% c("temp_24h_Den","pressure_24h_Den",
"humidity_24h_Den","wind_speed_24h_Den","clouds_all_24h_Den","weather_main_24h_Den_Dummy","Question.1")
dat.train24<-dat.train[dat.train24x]

dat.test24x <- names(dat.test) %in% c("temp_24h_Den","pressure_24h_Den",
"humidity_24h_Den","wind_speed_24h_Den","clouds_all_24h_Den","weather_main_24h_Den_Dummy","Question.1") 
dat.test24<-dat.test[dat.test24x]

dat.train12x <- names(dat.train) %in% c("temp_12h_Den","pressure_12h_Den",
"humidity_12h_Den","wind_speed_12h_Den","clouds_all_12h_Den",
"weather_main_12h_Den_Dummy","weather_main_24h_Den_Dummy",
"pressure1224","humidity1224",
"temp1224","wind_speed1224","clouds_all1224","Question.1")
dat.train12<-dat.train[dat.train12x]

dat.test12x <- names(dat.test) %in% c("temp_12h_Den","pressure_12h_Den",
"humidity_12h_Den","wind_speed_12h_Den","clouds_all_12h_Den",
"weather_main_12h_Den_Dummy","weather_main_24h_Den_Dummy",
"pressure1224","humidity1224",
"temp1224","wind_speed1224","clouds_all1224","Question.1") 
dat.test12<-dat.test[dat.test12x]


dat.train6x <- names(dat.train) %in% c("temp_6h_Den","pressure_6h_Den","humidity_6h_Den","wind_speed_6h_Den",
"clouds_all_6h_Den","weather_main_6h_Den_Dummy",
"weather_main_12h_Den_Dummy","weather_main_24h_Den_Dummy","pressure624",
"humidity624","temp624","wind_speed624","clouds_all624","pressure612",
"humidity612","temp612","wind_speed612","clouds_all612","Question.1") 
dat.train6<-dat.train[dat.train6x]

dat.test6x <- names(dat.test) %in% c("temp_6h_Den","pressure_6h_Den","humidity_6h_Den","wind_speed_6h_Den",
"clouds_all_6h_Den","weather_main_6h_Den_Dummy",
"weather_main_12h_Den_Dummy","weather_main_24h_Den_Dummy","pressure624",
"humidity624","temp624","wind_speed624","clouds_all624","pressure612",
"humidity612","temp612","wind_speed612","clouds_all612","Question.1") 
dat.test6<-dat.test[dat.test6x]

dat.train3x <- names(dat.train) %in% c("temp_3h_Den","pressure_3h_Den","humidity_3h_Den",
"wind_speed_3h_Den","clouds_all_3h_Den","weather_main_3h_Den_Dummy",
"weather_main_6h_Den_Dummy","weather_main_12h_Den_Dummy","weather_main_24h_Den_Dummy",
"pressure324","humidity324","temp324","wind_speed324","clouds_all324",
"pressure312","humidity312","temp312","wind_speed312","clouds_all312",
"pressure36","humidity36","temp36","wind_speed36","clouds_all36","Question.1") 
dat.train3<-dat.train[dat.train3x]

dat.test3x <- names(dat.test) %in% 
  c("temp_3h_Den","pressure_3h_Den","humidity_3h_Den",
"wind_speed_3h_Den","clouds_all_3h_Den","weather_main_3h_Den_Dummy",
"weather_main_6h_Den_Dummy","weather_main_12h_Den_Dummy","weather_main_24h_Den_Dummy",
"pressure324","humidity324","temp324","wind_speed324","clouds_all324",
"pressure312","humidity312","temp312","wind_speed312","clouds_all312",
"pressure36","humidity36","temp36","wind_speed36","clouds_all36","Question.1") 
dat.test3<-dat.test[dat.test3x]

dat.train1x <- names(dat.train) %in% c("temp_1h_Den","pressure_1h_Den",
"humidity_1h_Den","wind_speed_1h_Den","clouds_all_1h_Den","weather_main_1h_Den_Dummy",
"weather_main_3h_Den_Dummy","weather_main_6h_Den_Dummy","weather_main_12h_Den_Dummy",
"weather_main_24h_Den_Dummy","pressure124","humidity124","temp124","wind_speed124",
"clouds_all124","pressure112","humidity112","temp112","wind_speed112",
"clouds_all112","pressure16","humidity16","temp16","wind_speed16",
"clouds_all16","pressure13","humidity13","temp13","wind_speed13",
"clouds_all13","Question.1") 
dat.train1<-dat.train[dat.train1x]

dat.test1x <- names(dat.test) %in% c("temp_1h_Den","pressure_1h_Den",
"humidity_1h_Den","wind_speed_1h_Den","clouds_all_1h_Den","weather_main_1h_Den_Dummy",
"weather_main_3h_Den_Dummy","weather_main_6h_Den_Dummy","weather_main_12h_Den_Dummy",
"weather_main_24h_Den_Dummy","pressure124","humidity124","temp124","wind_speed124",
"clouds_all124","pressure112","humidity112","temp112","wind_speed112",
"clouds_all112","pressure16","humidity16","temp16","wind_speed16",
"clouds_all16","pressure13","humidity13","temp13","wind_speed13",
"clouds_all13","Question.1") 
dat.test1<-dat.test[dat.test1x]


```

```{r}
# include MASS library so we can use stepAIC

	library(MASS)

	mod.int <- glm(as.factor(Question.1) ~ 1, family=binomial(), data=dat.train24)
	mod.full <- glm(as.factor(Question.1) ~ .,family=binomial() ,data=dat.train24)
```
	
```{r}
	# forward selection
	stepAIC(mod.int, direction="forward",
              scope=list(lower=mod.int, upper= mod.full))
	ans.forward <- stepAIC(mod.int, direction="forward",
              scope=list(lower=mod.int, upper= mod.full))

	predicted.y <- as.matrix(cbind(rep(1,nrow(dat.test)),dat.test[,names(ans.forward$coefficients)[-1]])) %*% ans.forward$coef
	pe <- mean( (dat.test$Question - predicted.y)^2 )
pe
```
	
```{r}
	# backward selection
stepAIC(mod.full,direction="backward",
             scope=list(lower=mod.int, upper= mod.full))
ans.backward <- stepAIC(mod.full,direction="backward",
             scope=list(lower=mod.int, upper= mod.full))
```
	
```{r}
	# stepwise selection
stepAIC(mod.int, direction="both",
             scope=list(lower=mod.int, upper= mod.full))
```

```{r}
	mod.int <- glm(as.factor(Question.1) ~ 1, family=binomial(), data=dat.train12,control = list(maxit = 50))
	mod.full <- glm(as.factor(Question.1) ~ .,family=binomial() ,data=dat.train12,control = list(maxit = 50))
```
	
```{r}
	# forward selection
	stepAIC(mod.int, direction="forward",
              scope=list(lower=mod.int, upper= mod.full))
	ans.forward <- stepAIC(mod.int, direction="forward",
              scope=list(lower=mod.int, upper= mod.full))

	predicted.y <- as.matrix(cbind(rep(1,nrow(dat.test)),dat.test[,names(ans.forward$coefficients)[-1]])) %*% ans.forward$coef
	pe <- mean( (dat.test$Question - predicted.y)^2 )
pe
```
	
```{r}
	# backward selection
stepAIC(mod.full,direction="backward",
             scope=list(lower=mod.int, upper= mod.full))
ans.backward <- stepAIC(mod.full,direction="backward",
             scope=list(lower=mod.int, upper= mod.full))
```
	
```{r}
	# stepwise selection
stepAIC(mod.int, direction="both",
             scope=list(lower=mod.int, upper= mod.full))
```


```{r}
	mod.int <- glm(as.factor(Question.1) ~ 1, family=binomial(), data=dat.train6,control = list(maxit = 100))
	mod.full <- glm(as.factor(Question.1) ~.,family=binomial() ,data=dat.train6,control = list(maxit = 1000))
```
	
```{r}
	# forward selection
	stepAIC(mod.int, direction="forward",
              scope=list(lower=mod.int, upper= mod.full))
	ans.forward <- stepAIC(mod.int, direction="forward",
              scope=list(lower=mod.int, upper= mod.full))

	predicted.y <- as.matrix(cbind(rep(1,nrow(dat.test)),dat.test[,names(ans.forward$coefficients)[-1]])) %*% ans.forward$coef
	pe <- mean( (dat.test$Question - predicted.y)^2 )
pe
```
	
```{r}
	# backward selection
stepAIC(mod.full,direction="backward",
             scope=list(lower=mod.int, upper= mod.full))
ans.backward <- stepAIC(mod.full,direction="backward",
             scope=list(lower=mod.int, upper= mod.full))
```
	
```{r}
	# stepwise selection
stepAIC(mod.int, direction="both",
             scope=list(lower=mod.int, upper= mod.full))
```

```{r}
	mod.int <- glm(as.factor(Question.1) ~ 1, family=binomial(), data=dat.train3,control = list(maxit = 100))
	mod.full <- glm(as.factor(Question.1) ~.,family=binomial() ,data=dat.train3,control = list(maxit = 100))

```
	
```{r}
	# forward selection
	stepAIC(mod.int, direction="forward",
              scope=list(lower=mod.int, upper= mod.full))
	ans.forward <- stepAIC(mod.int, direction="forward",
              scope=list(lower=mod.int, upper= mod.full))

	predicted.y <- as.matrix(cbind(rep(1,nrow(dat.test)),dat.test[,names(ans.forward$coefficients)[-1]])) %*% ans.forward$coef
	pe <- mean( (dat.test$Question - predicted.y)^2 )
pe
```
	
```{r}
	# backward selection
stepAIC(mod.full,direction="backward",
             scope=list(lower=mod.int, upper= mod.full))
ans.backward <- stepAIC(mod.full,direction="backward",
             scope=list(lower=mod.int, upper= mod.full))
```
	
```{r}
	# stepwise selection
stepAIC(mod.int, direction="both",
             scope=list(lower=mod.int, upper= mod.full))
```
```{r}
	mod.int <- glm(as.factor(Question.1) ~ 1, family=binomial(), data=dat.train1,control = list(maxit = 100))
	mod.full <- glm(as.factor(Question.1) ~.,family=binomial() ,data=dat.train1,control = list(maxit = 100))

```
	
```{r}
	# forward selection
	stepAIC(mod.int, direction="forward",
              scope=list(lower=mod.int, upper= mod.full))
	ans.forward <- stepAIC(mod.int, direction="forward",
              scope=list(lower=mod.int, upper= mod.full))

	predicted.y <- as.matrix(cbind(rep(1,nrow(dat.test)),dat.test[,names(ans.forward$coefficients)[-1]])) %*% ans.forward$coef
	pe <- mean( (dat.test$Question - predicted.y)^2 )
pe
```
	
```{r}
	# backward selection
stepAIC(mod.full,direction="backward",
             scope=list(lower=mod.int, upper= mod.full))
ans.backward <- stepAIC(mod.full,direction="backward",
             scope=list(lower=mod.int, upper= mod.full))
```
	
```{r}
	# stepwise selection
stepAIC(mod.int, direction="both",
             scope=list(lower=mod.int, upper= mod.full))
```

#	library(leaps) #  See ?leaps for more info

#	ans <- leaps(x= dat.train24[1:ncol(dat.train24)-1], y=dat.train24[,ncol(dat.train24)], method="r2")
#	ans2 <- leaps(x= dat.train24[1:ncol(dat.train24)-1], 
#	 y=dat.train24[,ncol(dat.train24)], method="adjr2")
	
#	cat(names(dat.train24)[1:ncol(dat.train24)-1],"r2\n")
#temporary<-cbind(id=1:nrow(dat.train24),ans$which, r2=round(ans$r2,4), #adjr2=round(ans2$adjr2,4))
#temporary2<-data.frame(n.pred=row.names(temporary), temporary)

#r2.max=adjr2.max=c()
#	for(i in 1:ncol(dat.train24)-1){
#		r2.max<-c(r2.max,max(temporary[row.names(temporary)==i,"r2"]))
#		adjr2.max<-c(adjr2.max,max(temporary[row.names(temporary)==i,"adjr2"]))
#	}
	
#	plot(x=1:ncol(dat.train24)-1,y=r2.max, ylab="R2 (black), adjusted R2 (red)", xlab="# of predictors")
#	points(x=1:ncol(dat.train24)-1,y=adjr2.max, col="red")
#	abline(h=max(r2.max), lty=2)
#	abline(h=max(adjr2.max), lty=2, col="red")
	
	##r2.max
	##adjr2.max

# how well did the models do?

#	forward.stepwise <- predict.lm(ans.forward, newdata=dat.test[,1:ncol(dat.train24)-1])
#	mse.forward.stepwise <- mean((forward.stepwise - dat.test$Question)^2)

#	backward <- predict.lm(ans.backward, newdata=dat.test[,1:ncol(dat.train24)-1])
#	mse.backward <- mean((backward - dat.test$Question)^2)
	
#	mse.best.subsets <- NULL
#for(i in 1:ncol(dat.train24)-1){
#	temporary.best<-temporary2[temporary2$n.pred==i & temporary2$r2==r2.max[i],"id"]
#	mod.best<- lm(Question ~ ., #data=dat.train[,c(c(1:ncol(dat.train24)-1)*ans$which[temporary.best,],col(dat.train24)#)])

#	test.fitted <- predict.lm(mod.best, newdata=dat.test[,1:ncol(dat.train24)-1])
#	mse.best.subsets <-  c(mse.best.subsets,mean((test.fitted - dat.test$Question)^2))
#}##end subset loop


#	cbind(1:ncol(dat.train24)-1, mse.best.subsets)
#	mse.forward.stepwise 
#	mse.backward 

```
