```{r}
require(caTools)
dat<-FinalDat
set.seed(101) 
sample = sample.split(dat$dt, SplitRatio = .75)
trainset = subset(dat, sample == TRUE)
testset  = subset(dat, sample == FALSE)

	ans24hrs <- glm(as.factor(Question) ~
temp_24h_Den
+pressure_24h_Den+humidity_24h_Den+wind_speed_24h_Den
+rain_1h_24h_Den+rain_3h_24h_Den+snow_1h_24h_Den
+snow_3h_24h_Den+clouds_all_24h_Den
+weather_main_24h_Den
, family=binomial(), data=trainset)

#	ans24hrs <- glm(as.factor(Question) ~
#temp_24h_Den
#+pressure_24h_Den+humidity_24h_Den+wind_speed_24h_Den
#+rain_1h_24h_Den+rain_3h_24h_Den+snow_1h_24h_Den
#+snow_3h_24h_Den+clouds_all_24h_Den
#+weather_main_24h_Den
#, family=binomial(), data=dat_sample)

#	ans1hrs <- glm(as.factor(Question) ~
#temp_1h_Den
#+pressure_1h_Den+humidity_1h_Den+wind_speed_1h_Den
#+clouds_all_1h_Den
#, family=binomial(), data=dat_sample)
	
summary(ans24hrs)
```

```{r}
	ans12hrs <- glm(as.factor(Question) ~
temp_12h_Den
+pressure_12h_Den+humidity_12h_Den+wind_speed_12h_Den
+rain_1h_12h_Den+rain_3h_12h_Den+snow_1h_12h_Den
+snow_3h_12h_Den+clouds_all_12h_Den
+weather_main_12h_Den+I(pressure_12h_Den-pressure_24h_Den)+I(temp_12h_Den-temp_24h_Den)
, family=binomial(), data=dat_sample)
	
summary(ans12hrs)
plot(ans12hrs)
```


	# drop alcohol

	ans <- glm(as.factor(chd) ~ sbp + tobacco + ldl + famhist + obesity + age, 
                  family=binomial(), data=dat)
	summary(ans)

	# drop sbp

	ans <- glm(as.factor(chd) ~ tobacco + ldl + famhist + obesity + age, 
                  family=binomial(), data=dat)
	summary(ans)

	# drop obesity

	ans <- glm(chd ~ tobacco + ldl + famhist + age, 
                  family=binomial(), data=dat)
	summary(ans)
	exp(ans$coef)

	# alternatively the stepAIC procedure can also 
	# be used
	library(MASS)

	mod.int <- glm(chd ~ 1, family=binomial(), data=dat)
	mod.full <- glm(as.factor(chd) ~ sbp + tobacco + ldl + famhist + obesity + alcohol + age, 
                  family=binomial(), data=dat)

	stepAIC(mod.full, scope=list(upper=mod.full, lower=mod.int),
              direction="backward")

# let's get predictions
# note that I'm looking at the training set
# for an unbiased estimate of the MPE we
# need to form an independent test set

	ans2 <- predict(ans, dat, type="response")
	assigned.group <- ans2 > 0.5
	table(assigned.group, dat$chd)
	mean(assigned.group != dat$chd)

# let's look at relationships among the predictors

	library(lattice)
	splom(dat[,c(3,4,10)])

png("plots_heartdisease_ex/family_history_boxplots.png", width=1200,height=400)
	par(mfrow=c(1,3), mai=c(.8,.8,.2,.2))
	boxplot(dat$tobacco ~ dat$famhist, xlab="Family History", ylab="Tobacco", cex=2, cex.axis=2,cex.lab=2)
	boxplot(dat$ldl ~ dat$famhist, xlab="Family History", ylab="LDL", cex=2, cex.axis=2,cex.lab=2)
	boxplot(dat$age ~ dat$famhist, xlab="Family History", ylab="Age", cex=2, cex.axis=2,cex.lab=2)
dev.off()

	X <- dat[,c(3,4,10)]
	cor(X, use="pairwise.complete.obs")
	
	t.test(dat$tobacco ~ dat$famhist)
	t.test(dat$ldl ~ dat$famhist)
	t.test(dat$age ~ dat$famhist)


# for outcomes with more than 2 levels, we can use the
# multinom function in the nnet package to FIT the model

	library(nnet)

	ans <- multinom(chd ~ sbp + tobacco + ldl + famhist + obesity + alcohol + age, 
                    data=dat)
	ans
	names(ans)
	summary(ans)
	ans2 <- summary(ans)
	ans2$coefficients/ans2$standard.errors
	Z <- ans2$coefficients/ans2$standard.errors
	2*(1-pnorm(abs(Z)))
	
## same results as glm function!!###	
	summary(glm(as.factor(chd) ~ sbp + tobacco + ldl + famhist + obesity + alcohol + age, family=binomial(), data=dat))

# PREDICTION STEP

	pred.chd <- predict(ans, dat)
	temp<-	table(pred.chd, dat$chd)
	(temp[2,1]+temp[1,2])/sum(temp)


###############################  IRIS DATA  ##########################################

#############	
	ans <- multinom(Species ~ Sepal.Length+Sepal.Width+Petal.Length+Petal.Width,
                    data=iris)
	ans
	summary(ans)
	ans2 <- summary(ans)
	ans2$coefficients/ans2$standard.errors
	Z <- ans2$coefficients/ans2$standard.errors
	2*(1-pnorm(abs(Z)))

# PREDICTION STEP
library(psych)  ## for trace function

	pred.sp <- predict(ans, iris)
	temp<-table(pred.sp, iris$Species)
	(sum(temp)-tr(temp))/sum(temp)

########	
	iris$dif_ref<-ifelse(iris$Species=="virginica","1-virginica", ifelse(iris$Species=="versicolor","2-versicolor","3-setosa"))
ans <- multinom(dif_ref ~ Sepal.Length+Sepal.Width+Petal.Length+Petal.Width,
                    data=iris)
	ans
	ans2 <- summary(ans)
	ans2$coefficients/ans2$standard.errors
	Z <- ans2$coefficients/ans2$standard.errors
	2*(1-pnorm(abs(Z)))
	
# PREDICTION STEP
library(psych)  ## for trace function

	pred.sp <- predict(ans, iris)
	temp<-table(pred.sp, iris$dif_ref)
	(sum(temp)-tr(temp))/sum(temp)

	splom(iris,cex=0.6,pscales=0)
	round(cor(iris[,1:4]),2)


##############  testing nested models  ##############
null_model<-multinom(Species~1,data=iris)
ans <- multinom(Species ~ Sepal.Length+Sepal.Width+Petal.Length+Petal.Width,
                    data=iris)

x2<-deviance(null_model)-deviance(ans)
x2

### parameters for null model is 2 intercept terms, parameters for full model is 2 intercept terms + 4x2 parameters for the slope = 10 (count the coefficients); 10-2 = 8 
pchisq(x2,df=8,lower.tail=F)


nested_model<-multinom(Species~Sepal.Length+Sepal.Width+Petal.Length,data=iris)
ans <- multinom(Species ~ Sepal.Length+Sepal.Width+Petal.Length+Petal.Width,
                    data=iris)

x2<-deviance(nested_model)-deviance(ans)
x2

pchisq(x2,df=2,lower.tail=F)


